References

### 2015-01-06 cv/XieXiaolei-Academic.tex
Worked on EVT final test.

\begin{minipage}[t]{0.5\textwidth}
  Phone: +46 76 060 6638 \\
  Email: \href{mailto:xie.xiaolei@gmail.com}{\tt xie.xiaolei@gmail.com} \\
  Address: Kiviksgatan 7C, 21440 Malm\"{o}, Sweden
  Citizenship: Sweden \\
\end{minipage}

@@

\section*{Employment}
\begin{itemize}
\item Research Assistant, Lund University, June 10, 2014 - September
  30, 2014

  Based on the results from my thesis work, Prof. \AA berg and I wrote
  a paper together. Titled ``Effect of Heteroscedasticity on the
  spectrum of an Empirical Covariance Matrix'', we argued that, in
  certain circumstances, autocorrelations in the conditional
  volatilities were manifest in the empirical covariance matrixes'
  spectrum only through the unconditional distribution of the
  volatilities. In these circumstances, we derived in the case of small
  autocorrelations the spectrum of an empirical covariance matrix. The
  derivations were based on results from free probability theory.

\item Software Engineer, April 2004 - January 2011, Helsinki

I worked in the IT industry as a software engineer. I designed and
implemented software solutions in C, C++ and Java.

\end{itemize}

\section*{Skills}
\begin{itemize}
\item {\bf Programming:} Proficient in C, C++, Java, Matlab
\item {\bf Scientific writing:} Latex
\end{itemize}

>>>>

\begin{minipage}[t]{0.5\textwidth}
  Phone: +46 70 489 0472 \\
  Email: \href{mailto:xie.xiaolei@gmail.com}{\tt xie.xiaolei@gmail.com} \\
  Address: Kiviksgatan 7C, 21440 Malm\"{o}, Sweden
  Citizenship: Sweden \\
\end{minipage}

@@

\section*{Employment}
Between April 2004 and January 2011 I worked in the software industry
as a software engineer. I designed and implemented software solutions
in C, C++ and Java.

\section*{Skills}
\begin{itemize}
\item {\bf Programming:} Proficient in C/C++, Java, Matlab
\item {\bf Scientific writing:} Latex
\end{itemize}
